---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# indirectfacilitation

The goal of indirectfacilitation is to ...

## Installation

You can install indirectfacilitation from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("alaindanet/indirect_facilitation_model")
```

## Example

This is a basic example which shows you how to solve a common problem:


- Load the packages:

```
devtools::load_all()

library(simecol)
library(ggplot2)
library(tibble)
library(magrittr)
```

- Load the model and specify the parameters:

```
mod <- two_facilitation_model()
mod

# Show parameters:
parms(mod)

# Tweak parameters:
parms(mod)["g"] <- 0.2
parms(mod)["gamma1"] <- 0.10
parms(mod)["u"] <- 5 
times(mod) <- c(from = 0, to = 1000, by = 1)
```

- Launch a simulation and plot the result:

```
mod_run <- sim(mod)
plotnp(mod_run)
```

## Todo

### Paper 

- Fig 1: methods
- Fig 2: multi-states + bifurcation details
- Fig 3: cellular automata, spatial coexistence Cnp $f(\gamma, u)$ 

### Implementation

- [ ] sim_multi():
    - [ ] Save a simecol object
    - [ ] Save a time argument
    - [ ] Save init values
    - [ ] Save baseline parameters 
    - [ ] Save param_combination
    - [ ] param_combination: matrix of parameter combination
    - [ ] be able to sim from a sim_multi object
- [ ] Generalize run_scenarii_gradient and run_2d_gradient: f(b,g)
    - [ ] check_param(model_spec, names(gradient)))
    - [ ] Add check for argument conformity (check_param, check_inits)
      of valid starting values (scenario = "custom"), or a named list (provided by init_scenarii())
    - [ ] Add methods: init.scenarii(), param.scenarii() (S4 methods)
      https://stackoverflow.com/questions/12100856/combining-s4-and-s3-methods-in-a-single-function
- [ ] plot: separate lines (create groups: e.g: together & < threshold, together & >= threshold, low_together ...)
    - [ ] See [here](https://stackoverflow.com/a/23863893/5968131) 
- [x] Compare the effect of dispersal, facilitation strength, paturâge, aridité on clustering  
- [ ] Document functions
- [x] Check if simulations have reached stability
    - [x] Implementation of a custom solver ("lsodar")
    - [x] Test the implementation

