---
title: "Definition of the associative protection"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = TRUE}
library(tidyverse)
library(magrittr)
```


# Definition of the associative protection $n = f(\gamma)$  

## In previous papers

Le Galliard et al. (2003) models the cost of altruism as: 

$$ 
\gamma = Kn^{u}
$$

with $n$, the level of altruism, $u$, the shape of the relationship between the
associative protection and $\gamma$, the cost.

Lion et al. (2007) used the same kind of relationship but assumed that the cost
is dependant of the environment (i.e. of the neighboring cells).

```{r, fig.width = 7, fig.height = 5}
gamma_lion <- function(n, u = 0.3, K = 1) {
  K*n^u
}
factors <- list(n = seq(0, 1, .05), u = c(.5, 1.5))
df <- expand.grid(factors)
df %<>% dplyr::mutate(
  gamma1 = purrr::map2_dbl(n,u, gamma_lion),
  u = as.factor(u)
  )

p <- ggplot(df, aes(x = n, y = gamma1, group = u))
p + geom_line(aes(colour = u), linetype = 1) +
  labs(y = expression(paste("Cost of the defence (", gamma, ")")), 
    x = expression(paste("Altruistic trait (", n, ")")), 
    title = "Lion et al. (2003) relationship")
```

## Exponential relationship  
 
In our case, we can assume that there is a relationship between the maximal associative
protection and the cost of the defence ($\gamma$). The level of maximal
associative protection ($n$) is defined as the relative decrease of grazing
effect when a sapling is surrounded by four nurse plants ($q_{N|0} = 1$, so
effective associative protection becomes $n*q_{N|0} = n$).

Let $n(\gamma) = 1 - e^{-\tau\gamma}$

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
#Function
gamma_asymp <- function(gamma1, tau = 20) {
  1 - exp(-tau*gamma1)
}

#Data
factors <- list(gamma1 = seq(0, 1, .01), tau = c(5, 20))
df <- expand.grid(factors) 
df %<>% 
  dplyr::mutate(
  n = purrr::map2_dbl(gamma1, tau, gamma_asymp),
  tau = as.factor(tau)
  )

#Plot
p <- ggplot(df, aes(x = gamma1, y = n, group = tau))
p + geom_line(aes(colour = tau), linetype = 1) +
  labs(
    y = expression(paste("Maximum level of associative protection (", n, ")")),
    x = expression(paste("Cost of the defence (", gamma, ")")), 
    title = "Relationship between the cost of defence and the maximum level of
    associative protection")
```

The resulting protection against grazing is given by $n*q_{N|0}$. The
resulting decrease in mortality due to grazing is maximal when both $n = 1$ and
$q_{N|0} = 1$ meaning that the protegee sapling is surrounded by four nurse
plant. 

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
#Function
linear_protection_inc <- function(q_n0, n = 1) {
  1 -  q_n0*n
}

#Data
factors <- list(q_n0 = seq(0, 1, .25), n = seq(0, 1, 0.25))
df <- expand.grid(factors) 
df %<>% 
  dplyr::mutate(
  protection = purrr::map2_dbl(q_n0, n, linear_protection_inc),
  n = as.factor(n)
  )

#Plot
p <- ggplot(df, aes(x = q_n0, y = protection, group = n))
p + geom_line(aes(colour = n), linetype = 1) +
  labs(
    y = expression(paste("Level of effective protection (", n*q[N0], ")")),
    x = expression(paste("Relative number of neighbors (", q[N0], ")")), 
    title = "Relationship between the neighborhood of a cell and the effective 
    level of associative protection")
```

* * * * *


This protection type is really weak and we might want to increase it. The
maximum effective protection $n*q_{N|0}$ when a protegee
sapling is surrounded by one adult nurse $q_{N|0}$ is $.25$.
We can define an function $f(\gamma)$ which reach a maximum earlier but which is
restricted to $1$. 

The mortality due to grazing is defined like this: 
$$
g(1 - n*q_{N|0})
$$

Let define it as a function of protection function:
$$
g(1 - p)
$$

A protection function which is restricted to 1:

$$
p = (1 - e^{- \tau * q_{N0}})
$$

with $p$ being the mortality of the sapling due to grazing depending notably on
the presence of the nurse.

For example, we could say in case of a very good protection, the risk to be
killed by grazers when there is one neighbor is 5\% of the base rate.

We might want compute $\tau$ to define a given level of protection for a sapling
surrounded by one nurse ($q_{N0} = .25$):

$$
\tau = \frac{ log(\frac{ -1 }{ p - 1 })}{ q }
$$

```{r, echo = FALSE}
compute_tau <- function(p = 9/10, q = 1/4) {
  log(-1/(p - 1))/q
}
```

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
exp_grazing_protection <- function(q_n0, tau = 20) {
  1 - exp(- tau * q_n0) 
}

factors <- list(
  q_n0 = seq(0, 1, .25),
  tau = compute_tau(
    p = c(1/4, 1/2, 3/4, 9/10), 
    q = 1/4)
  )
df <- expand.grid(factors) 
df %<>% 
  dplyr::mutate(
  protection = purrr::map2_dbl(q_n0, tau, exp_grazing_protection),
  tau = as.factor(tau)
  )

#Plot
p <- ggplot(df, aes(x = q_n0, y = protection, group = tau))
p + geom_line(aes(colour = tau), linetype = 1) +
  labs(
    y = expression(paste("Level of effective protection (", 1 - e^(- tau * q[N0]),
	")")), 
    x = expression(paste("Relative number of neighbors (", q[N0], ")")), 
    title = "Relationship between the neighborhood of a cell and the effective
    level of associative protection")
```

Let's now exam how the protection can be linked to the cost of defense. We
introduce $p_{\frac{1}{z}}$, which is the effective protection when a protegee is
surrounded by one nurse plant.

$$
p_{\frac{1}{z}}(\gamma) \in [0,1]
$$

We can define the relationship between $p_{\frac{1}{z}}$ and $\gamma$: 

$$
p_{\frac{1}{z}}(\gamma) = 1 - e^{- u \gamma} 
$$

It cost only one parameter ($u$)! With $q$ and $p$ known, $\tau$ is easily
computed and so the level of protection depending on $q_{N|0}$.

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
compute_p_one_z <- function(gamma1, u) {
 1 - exp(- u * gamma1)
}

factors <- list(
  gamma1 = seq(0, .2, .01),
  u = seq(5, 20, 4)
  )

df <- expand.grid(factors) 
df %<>% 
  dplyr::mutate(
  tau = purrr::pmap_dbl(list(gamma1, u), compute_p_one_z),
  u = as.factor(u),
  )

#Plot
p <- ggplot(df, aes(x = gamma1, y = tau))
p + geom_line(aes(colour = u)) +
  labs(
    y = expression(paste("Relative decrease of mortality due to grazing when surrounded by one neighbor ","(", p[frac(1,z)], ")")), 
    x = expression(paste("Cost of defense (", gamma, ")")), 
    title = "Relationship between the protection provided by one neighbor and
    the cost of defense")
```
