---
title: "Definition of the three state model"
author: "Alain Danet"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

* We have 3 states ($N$, $P$, $0$).
* We have six differeNt pairs ($\rho_{NN}$, $\rho_{N0}$, $\rho_{NP}$,
  $\rho_{PP}$, $\rho_{P0}$, $\rho_{00}$) since $\rho_{\sigma\sigma'} =
  \rho_{\sigma'\sigma}$.

* We have four coNservatioN equatioNs:
  1. $\rho_{N} + \rho_{0} + \rho_{P} = 1$
  2. $\rho_{N} = \rho_{NN} + \rho_{N0} + \rho_{NP}$
  3. $\rho_{0} = \rho_{00} + \rho_{N0} + \rho_{P0}$
  4. $\rho_{P} = \rho_{PP} + \rho_{P0} + \rho_{NP}$
* There are 3 singleton variables: $\rho_{N}$, $\rho_{0}$, $\rho_{P}$

So we need $6+3-4 = 5$ equations to solve this system:

 * $\frac{d\rho_{NN}}{dt}$
 * $\frac{d\rho_{NP}}{dt}$
 * $\frac{d\rho_{PP}}{dt}$
 * $\frac{d\rho_{N}}{dt}$
 * $\frac{d\rho_{P}}{dt}$

### Transition equations

$$
w_{0,N|P} = (\delta \rho_{N} + (1-\delta) \frac{(z-1)}{z} \times \frac{ \rho_{N0}
}{\rho_{0}}) \times (b - c\rho_{+} - \gamma)
$$

$$
w_{0,N|N} = (\delta \rho_{N} + \frac{(1-\delta)}{z} +  (1-\delta) \frac{(z-1)}{z} \frac{\rho_{N0}}{\rho_{0}}) \times (b - c\rho_{+} - \gamma)
$$

$$
w_{0,N} = (\delta \rho_{N} + (1-\delta) \frac{\rho_{N0}}{\rho_{0}}) \times (b - c\rho_{+} - \gamma)
$$

$$
w_{0,P} = (\delta \rho_{P} + (1 - \delta) \frac{\rho_{P0}}{\rho_{0}})
\times (b - c\rho_{+} - g(1 - \frac{\rho_{N0}}{\rho_{0}}f(\gamma)))
$$

$$
w_{0,P|N} = (\delta\rho_{P} + (1 - \delta) \frac{z - 1}{z}
\frac{\rho_{P0}}{\rho_{0}}) \times (b - c\rho_{+} - g(1 -
(\frac{z - 1}{z} \frac{\rho_{N0}}{\rho_{0}} + \frac{1}{z})f(\gamma)))
$$

$$
w_{0,P|P} = (\delta\rho_{P} +\frac{1 - \delta}{z} + (1 - \delta) \frac{z-1}{z}
\frac{\rho_{P0}}{\rho_{0}}) \times (b - c\rho_{+} - g(1 -
\frac{(z-1)}{z} \frac{\rho_{N0}}{\rho_{0}}f(\gamma)))
$$

$$
w_{0,P} = (\delta\rho_{P} + (1 - \delta) \frac{\rho_{P0}}{\rho_{0}}) \times (b -
c\rho_{+} - g(1 - \frac{\rho_{N0}}{\rho_{0}}f(\gamma)))
$$

$$
w_{P,0} = w_{P,0} = m
$$

### ODEs system 

WARNING: I am not sure of the 2 times

$$
\begin{aligned}
\frac{d\rho_{NP}}{dt} = \rho_{P0} \times w_{0,N|P} + \rho_{N0} \times w_{0,P|N}
- \rho_{NP} \times (w_{P,0} + w_{N,0})
\end{aligned}
$$

$$
\begin{aligned}
\frac{d\rho_{PP}}{dt} = 2\rho_{P0} \times w_{0,P|P} - 2\rho_{PP} \times w_{P,0}\\
\end{aligned}
$$

$$
\begin{aligned}
\frac{d\rho_{NN}}{dt}= 2\rho_{N0} \times w_{0,N|N} - 2\rho_{NN} \times w_{N,0}  
\end{aligned}
$$

$$
\begin{aligned}
\frac{d\rho_{P}}{dt} = \rho_{0} \times w_{0,P} - \rho_{P} \times w_{P,0}
\end{aligned}
$$

$$
\begin{aligned}
\frac{d\rho_{N}}{dt} = \rho_{0} \times w_{0,N} - \rho_{N} \times w_{N,0}
\end{aligned}
$$

### Definition of the associative protection $n = f(\gamma)$  

Le Galliard et al. (2003) models the cost of altruism as: 

$$ 
\gamma = Kn^{u}
$$

with $n$, the level of altruism, $u$, the shape of the relationship between the
associative protection and $\gamma$, the cost.

Lion et al. (2007) used the same kind of relationship but assumed that the cost
is dependant of the environment (i.e. of the neighboring cells).

```{r, fig.width = 7, fig.height = 5}
gamma_lion <- function(n, K = 1, u = 0.3) {
  K*n^u
}
curve(gamma_lion(n = x, K = 1, u = 0.5), 0, 1,
  col = "blue", xlab = expression(n),
  ylab = expression(gamma),
  main = "Lion et al. (2003) relationship")
curve(gamma_lion(n = x, K = 1, u = 1.5), 0, 1,
  col = "green", add = TRUE)
```

 
In our case, we can assume that there is a relationship between the associative
protection and the cost of protection.

Let $n(\gamma) = 1 - e^{-\tau\gamma}$

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
gamma_asymp <- function(gamma1, tau = 20) {
  1 - exp(-tau*gamma1)
}
curve(gamma_asymp(gamma1 = x, tau = 20), 0, 1,
  col = "blue", xlab = expression(gamma),
  ylab = expression(n),
  main = "Choosen relationship")
curve(gamma_asymp(gamma1 = x, tau = 5), 0, 1,
  col = "green", add = TRUE)
```

The resulting protection against grazing is given by $n*q_{N|0}$. The
resulting decrease in mortality due to grazing is maximal when both $n = 1$ and
$q_{N|0} = 1$ meaning that the protegee sapling is surrounded by four nurse
plant. 

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
linear_protection_inc <- function(q_n0, n = 1) {
  1 -  q_n0*n
}
curve(linear_protection_inc(q_n0 = x, n = 1), 0, 1,
  col = "blue", xlab = expression(gamma),
  ylab = expression(1 - n * q[N0]),
  main = "Decrease of the grazing thanks to associative protection ")
curve(linear_protection_inc(q_n0 = x, n = .5), 0, 1,
  col = "green", add = TRUE)
```

This protection type is really weak and we might want to increase it. One
possibility could be to define a function which reach a maximum earlier but
which is restricted to 1. 

A function as below has those properties: 

$$
p = 1 - (1 - e^{- \tau * q_{N0}})
$$

with p being the mortality of the sapling due to grazing depending notably on
the presence of the nurse.

For example, we could say in case of a very good protection, the risk to be
killed by grazers when there is one neighbor. 

```{r, fig.width = 7, fig.height = 5, echo = FALSE}
exp_grazing_protection <- function(q_n0, tau = 20) {
  1 - exp(- tau * q_n0) 
}

curve(exp_grazing_protection(q_n0 = x, tau = 4*log(20)), 0, 1,
  col = "blue", xlab = expression(q[N0]),
  ylab = "decrease",
  main = "Decrease of the grazing thanks to associative protection ")
curve(exp_grazing_protection(q_n0 = x, tau = ), 0, 1,
  col = "green", add = TRUE)
```
