---
title: "Analyse model"
output:
  pdf_document:
    fig_width: 7
    fig_height: 6
    fig_caption: true
    toc: true
    toc_depth: 3
    highlight: zenburn 
    number_sections: true
---


# Pair approximation model with local competition

```{r, echo=FALSE}
source("~/Documents/thesis/thesis_chap1_model/code/analysis_function.r")
data <- read.table("output.csv", sep=",", row.names=1, header=T)
library(knitr)
```
## Equation used

Compared to the initial model we used here, we expressed competition as only local.

### Colonisation

#### Nurse species
\begin{equation}
	w_{ \left\{0,+_n \right\} } = \left( \delta_n\rho_{+_N} + \left( 1 - \delta_n \right)q_{+_n|0}\right) \left(b_n-c_nq_{+_n|+_n} -  c_{pn}q_{+_p|0} \right)
\end{equation}

#### Protégée species
\begin{equation}
	w_{ \left\{0,+_p \right\} } = \left( \delta_p\rho_{+_p} + \left( 1 - \delta_p \right)q_{+_p|0}\right) \left(b_p-c_pq_{+_p|0} -  c_{np}q_{+_n|0} - g(1 - q_{+_n|0}n) \right)
	\label{recolP}
\end{equation}

## Parameters used

```{r, echo=FALSE}
pars <- c("del","m","n","b","cn","cp","cnp","cpn","g")
parameters <- list()
for(i in 1:length(pars)){
	parameters[[i]] <- unique(as.vector(data[,pars[i]]))
}
names(parameters) <- pars
param <- t(as.data.frame(lapply(parameters,
				FUN=function(x){return(c(round(min(x),2),round(max(x),2))
)})))
colnames(param)  <- c("min", "max")

kable(param, caption="Listes des paramètres utilisées et de leur valeurs")
```

## Coexistence

### Effect of mortality

```{r, echo=FALSE, fig.cap="Green light: nurse alone, green dark: coexistence, black: protégée alone"}
par(mfrow=c(2,2))
m <- parameters$m
for(i in 1:4){
	diag.pairs(data  = data,
		   delta = 0.1,
		   cp    = 0.2,
		   cn    = 0.2,
		   cpn   = 0.45,
		   cnp   = 0.1,
		   m     = m[i],
		   n     = 1,
		   alpha = 150,
		   main = paste("m=",m[i],sep="")
		   )
}

```

### Effect of competitive ability of the protégée

```{r, echo=FALSE, fig.cap="Green light: nurse alone, green dark: coexistence, black: protégée alone"}
par(mfrow=c(2,3))
cpn <- parameters$cpn[9:length(parameters$cpn)]
for(i in 1:length(cpn)){
	diag.pairs(data  = data,
		   delta = 0.1,
		   cp    = 0.2,
		   cn    = 0.2,
		   cpn   = cpn[i],
		   cnp   = 0.1,
		   m     = 0.02,
		   n     = 1,
		   alpha = 150,
		   main = paste("cpn=",cpn[i],sep="")
		   )
}

```

## Co-occurences

### Statistics

Which parameter combination gives positive co-occurences (i.e. $Cnp >= 1.1$) between two species when the density of the two species is superior to 0?

```{r, echo=FALSE}
coex <- data[which(data$Cnp > 1.1 & data$rhon > 0.05 & data$rhop > 0.05),]
summary(coex[,c("m","n","b","cnp","cpn","g","Cnp")])
```
The positive co-occurences arises when the grazing pressure and the competition of the nurse on the protégée is also high. A longer lifespan seems also promote coexistence.


### The dynamic of co-occurences

```{r, echo=FALSE}
g   <- c(0.25, 0.75)
cpn <- c(0.35, 0.85)

par(mfrow=c(length(cpn),length(g)))
for(i in 1:length(g)){
	for(j in 1:length(cpn)){
	stab.pairs(data  = data,
	   delta = 0.1,
	   cp    = 0.2,
	   cn    = 0.2,
	   cpn   = cpn[j],
	   cnp   = 0.1,
	   m     = 0.02,
	   n     = 1,
	   g     = g[i],
	   alpha = 150,
	   main = paste("g=",g[i]," ","cpn=",cpn[j], sep=""))
	}
}

```

### Co-occurence diagram

```{r, echo=FALSE}
diag.c.pairs(data  = data,
	     delta = 0.1,
       	     cp    = 0.2,
	     cn    = 0.2,
	     cpn   = 0.85,
	     cnp   = 0.1,
	     m     = 0.02,
	     n     = 1,
	     alpha = 150,
	     main = "Co-occurences")
legend( x= 0.5, y=0.5,legend=seq(0,1.2,0.1), col=c(heat.colors(12)), pch=6)
```


# Cellular automata with local competition

```{r, echo=FALSE}
data <- read.table("~/Documents/thesis/thesis_chap1_model/simulation/CA_mod3/CA_output.csv", sep=",", row.names=1, header=T)
library(knitr)
hist(data$clus_2_1)
summary(data[data$clus_2_1 >=0.6 & data$rho_nurse >=0.05 & data$rho_protege >=0.05,
	c("rho_nurse", "rho_protege", "c_1", "c_2", "c_21", "c_12", "b", "m", "g","clus_2_1")])
```

## Parameters used

Same as pair approximation!

## Results

No positive co-occurence occurs! Fuck, fuck, fuck. Futhermore, the use of a low mortality ( m=  `r unique(data$m)`) made the vegetal cover very high.

```{r, echo=FALSE}

```
